---
title: "Home based anxiety interventions meta-analysis"
author: "Tamas Nagy"
date: "6/29/2020"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
editor_options: 
  chunk_output_type: console
bibliography: [references.bib]
---

```{r Packages & settings, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(encoding = 'UTF-8')

library(tidyverse)
library(readxl)
library(metafor)
library(metaviz)
library(dmetar)
library(janitor)
library(citr)

```

```{r Prep bibliography, eval=FALSE, include=FALSE}
# This does not have to be run
# Creates a tidy bibliography from the local bib file
citr::tidy_bib_file(messy_bibliography = "d:/Documents/Mendeley references/library.bib",
                    file = "references.bib", 
                    rmd_file = "index.Rmd",
                    encoding = "UTF-8")

```

[@Viechtbauer2010b]

```{r Load data}
cbt <- 
  read_excel("data/database_meta_anxiety.xlsx") %>% 
  clean_names()


```

I think in the CMA you used the "method-of-moments estimator". According to @Viechtbauer2005, it is better to use the restricted maximum likelihood estimator. Using this only slightly changes the results, but IMO it is a more appropriate and defensible choice.

```{r Build meta models}
# Model for the children self-report MA
selfrep_df <- 
  cbt %>% 
  filter(outcome == "children") 

mod_selfrep <-  rma(yi = hedges_g, 
      sei = se_hedges_g, 
      data = selfrep_df, 
      method = "REML")

mod_selfrep


# Model for the clinician rating MA
mod_rate <-
  cbt %>%
  filter(outcome == "clinician") %>%
  rma(yi = hedges_g,
      sei = se_hedges_g, 
      data = .,
      method = "REML")

mod_rate

# Create tables that will be added to the forest plot
selfrep_table <-
  cbt %>% 
  filter(outcome == "children") %>% 
  select(Study = study, N = sample_size)

selfrep_summary <- 
  selfrep_table %>% 
  group_by(name = "Aggregated effect") %>% 
  summarise(N = sum(N))

rate_table <-
  cbt %>%  
  filter(outcome == "clinician") %>% 
  select(Study = study, N = sample_size)

rate_summary <- 
  rate_table %>% 
  group_by(name = "Aggregated effect") %>% 
  summarise(N = sum(N))

```

# Forest plots

## Self-report
### Metafor

```{r fig.width = 9}
forest(mod_selfrep, 
       top = 3, 
       xlab = "Hedges' g", 
       slab = selfrep_table$Study,
       mlab = "Aggregated effect", 
       ilab = selfrep_table$N, 
       ilab.xpos = -1.5)
text(c(-3.9, -1.5, -0.5, 2.5, 5.3), 20, c("Study", "N","Favors control", "Favors intervention", "Hedges' [95%]"))

```

### metaviz

```{r fig.width = 9, warning = FALSE}
viz_forest(mod_selfrep, 
           study_table = selfrep_table,
           text_size = 4, 
           annotate_CI = TRUE, 
           xlab = "Hedges's g", 
           summary_table = selfrep_summary)
```


## Clinician rating

### metafor
```{r fig.width = 9}
forest(mod_rate, 
       top = 3, 
       xlab = "Hedges' g", 
       slab = rate_table$Study,
       mlab = "Aggregated effect", 
       ilab = rate_table$N, 
       alim = c(-2.5, 8),
       ilab.xpos = -4)
text(c(-11.5,-4, -1, 8, 17.9), 15, c("Study", "N","Favors control", "Favors intervention", "Hedges' [95%]"))
```

### metaviz

```{r fig.width = 9, warning = FALSE}
viz_forest(mod_rate, 
           study_table = rate_table,
           text_size = 3.5, 
           xlab = "Hedges'g", 
           summary_table = rate_summary,
           annotate_CI = TRUE)
```

# Funnel plots
## Self-report
### metafor

The first is a normal funnel plot, the second is a normal with trim-and-fill, the third is a contour enhanced funnel plot with trim-and-fill, centered on 0 (no effect). [@VanAssen2015a; @Peters2008]
```{r}
funnel(mod_selfrep, 
       shade=c("white", "gray55"),
       legend = TRUE)


trimfill(mod_selfrep) %>% 
  funnel(., 
         shade=c("white", "gray55"),
         legend = TRUE)

trimfill(mod_selfrep) %>% 
  funnel(., 
         level=c(90, 95), 
         shade=c("white", "gray55", "gray75"),
         refline=0,
         legend = TRUE)
```

As there seems to be some publication or small study bias, we can try to correct for that.
The model remains significant.
```{r}
trimfill(mod_selfrep)
```


### metaviz

This plot combines the zero centered contour funnel plot with the traditional funnel plot with the estimated effect (solid black vertical line), and the trim-and-fill adjusted aggregated effect size (dashed line). The TAF studies are filled, the real studies are hollow (I want to reverse that). 
```{r}
viz_funnel(mod_selfrep, 
           method = "RE",
           sig_contours = TRUE, 
           contours = TRUE,
           trim_and_fill = TRUE,
           text_size = 4
           ) +
  geom_vline(xintercept = 0, alpha = .2, color = "blue", size = 2)
  

```

## Clinician rating

There was no need for the trim-and-fill here, so it is not visualized, and ES is not adjusted.

### metafor

```{r}
funnel(mod_rate, 
       shade=c("white", "gray55"),
       legend = TRUE)

funnel(mod_rate, 
       level=c(90, 95), 
       shade=c("white", "gray55", "gray75"),
       refline=0,
       legend = TRUE)

```


### metaviz
```{r}
viz_funnel(mod_rate, 
           method = "RE",
           sig_contours = TRUE, 
           contours = TRUE,
           text_size = 4) +
  geom_vline(xintercept = 0, alpha = .2, color = "blue", size = 2)
```

# Outlier detection
## Self-report

```{r}
leave1out(mod_selfrep)
find.outliers(mod_selfrep)
```

## Clinician rating
```{r}
leave1out(mod_rate)
find.outliers(mod_rate)
```



# References  
